### 2016-10-12 analysis-note-v2/analysis-2.tex
created a directory for the final answers

>>>>

In addition to evaluating the systematic uncertainties on $A_{LU}$ at $\phi = 
90^{\circ}$, we performed bin by bin, in $\phi$, extraction of these 
uncertainties. For instance, regarding the bin extraction from the source 'data 
binning' listed in table \ref{Table:systematic_uncertainties}, the uncertainty 
is calculated as the difference between the two reconstructed asymmetries.  
Similar procedures have been carried out for the other studies, and finally all 
the contributions were added quadratically. These systematic uncertainties will 
be shown with the final asymmetry results in the following chapter.
